---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

Original dataset is [here](http://www.cdc.gov/brfss/annual_data/2013/files/LLCP2013ASC.ZIP)

Codebook for dataset is [here](https://www.cdc.gov/brfss/annual_data/2013/pdf/codebook13_llcp.pdf)

```{r delete}
if(!file.exists("./codebook2013.pdf")) {
     download.file("https://www.cdc.gov/brfss/annual_data/2013/pdf/codebook13_llcp.pdf",
                   destfile = "./codebook2013.pdf",
                   mode = "wb"
                   )
}
```

>Identify a research question similar to questions we’ve talked about in this course. Use the Behavioral Risk Factor Surveillance System (BRFSS) dataset (provided below).
All analysis must be completed using the R programming language via RStudio, and your write up must be an R Markdown document. To help you get started we provide a template Rmd file below. Download this file, and fill in each section.
Your project will consist of 3 parts:
Data: (3 points) Describe how the observations in the sample are collected, and the implications of this data collection method on the scope of inference (generalizability / causality). Note that you will need to look into documentation on the BRFSS to answer this question. See http://www.cdc.gov/brfss/ as well as the "More information on the data" section below.
Research questions: (11 points) Come up with at least three research questions that you want to answer using these data. You should phrase your research questions in a way that matches up with the scope of inference your dataset allows for. Make sure that at least two of these questions involve at least three variables. You are welcomed to create new variables based on existing ones. With each question include a brief discussion (1-2 sentences) as to why this question is of interest to you and/or your audience.
EDA: (30 points) Perform exploratory data analysis (EDA) that addresses each of the three research questions you outlined above. Your EDA should contain numerical summaries and visualizations. Each R output and plot should be accompanied by a brief interpretation.
In addition to these parts, there are also 6 points allocated to overall organization and readability of your project. Total points add up to 50 points. See the assessment rubric for more details on how your peers will evaluate your work.
Your submission should be a single HTML file that results from knitting your Rmd file. This document should contain all your code, R output and plots, and your narrative. You must use the Rmd template provided in the project instructions.
Review criterialess 
Do you understand the research question?
Is it clear how data can be used to answer this research question as its phrased?
Scope of inference - generalizability: Is the data collection explained clearly? Did the writer correctly identify the population of interest? Did the writer correctly decide whether the findings from this analysis can be generalized to that population, or, if not, a subsection of that population? Is their explanation satisfactory to make this decision? Are potential sources of bias discussed, and if so, is the discussion satisfactory?
Scope of inference - causality: Did the writer identify correctly whether these data can be used to establish causal links between the variables of interest. Is the explanation satisfactory?
Are the research questions well defined and is it clear why they are of interest to the author / audience? Are appropriate numbers of variables used in each research question?
Are appropriate summary statistics calculated, and are they explained/interpreted in context of the data and the research question?
Are appropriate visualizations included, and are they explained/interpreted in context of the data and the research question?
Did the writer address what the findings from the exploratory analysis suggest about the research question?

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data
```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data

```{r}
glimpse(brfss2013)
```

* * *

## Part 2: Research questions

**Research quesion 1:**

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

